Distribution-oblivious Programming with Dish

### 2019-09-21 pldi/draft.tex
Start examples

% \begin{lstlisting}[language=sh,float=h,numbers=none]
% cat doc.ms |                   # print input file
% groff -t -e -mandoc -Tascii |  # remove formatting
% col -bx |                      # remove backspaces 
% tr A-Z a-z |                   # convert to lower case
% tr -d '[:punct:]' |            # remove punctuation
% sort |                         # put words in alphabetical order
% unique |                       # remove duplicate words
% comm -13 /usr/share/dict -     # report words not in dictionary 
% \end{lstlisting}
% greece; stops
% AWS policy specification
\begin{lstlisting}[language=sh,float=h,numbers=none]
 cat * | tr -cs A-Za-z`\n` | tr A-Z a-z |
   sort | uniq -c | sort -rn | head 5 > out
\end{lstlisting}

@@

>>>>

% \begin{lstlisting}[language=sh,float=h,numbers=none]
% cat doc.ms |                   # print input file
% groff -t -e -mandoc -Tascii |  # remove formatting
% col -bx |                      # remove backspaces 
% tr A-Z a-z |                   # convert to lower case
% tr -d '[:punct:]' |            # remove punctuation
% sort |                         # put words in alphabetical order
% unique |                       # remove duplicate words
% comm -13 /usr/share/dict -     # report words not in dictionary 
% \end{lstlisting}
% greece; stops
% AWS policy specification
\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
 cat * | tr -cs A-Za-z`\n` | tr A-Z a-z |      (($$p_1$$))
   sort | uniq -c | sort -rn | head 5 > out
\end{lstlisting}

@@

This section breaks down $p_1$ to presents important background on and challenges
of shell scripting.

\subsection{Unix Pipelines, Informally}

Shell scripting

\heading{Basics}

\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
 ls -l | wc -l                                                  (($$p_2$$))
\end{lstlisting}

\heading{Generation}
\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
 cat * | wc -l > out.txt                                          (($$p_2$$))
\end{lstlisting}

\heading{Identifiers}
\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
 cat /proc/ >                                                   (($$p_2$$))
\end{lstlisting}

\heading{Stream Manipulation}
Explicit Redirection
Implicit splitting and merging 
This can be done through the file-system operators

\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
 cat /proc/ >                                                   (($$p_2$$))
\end{lstlisting}

\heading{Grouping}
Composition

The shell provides several ways of grouping commands and manipulating their
overall input and output channels

{ echo 1; echo 2; } > out.txt

\subsection{Comnands}

% Sets vs. Classes

Distributability classes, based on how

\heading{Preliminaries}

\heading{POSIX, GNU Core-utils, and beyond}

\heading{Stateless}

\heading{Pure}

\heading{File-system}

\heading{Side-effectful}

\heading{Irreversably Side-effectful}

\subsection{The Shell Language}

\heading{Implicits}
Expansion
Implicits
Context

\heading{Language Constructs}

Even without these, the Unix pipeline language is powerful enough to capture complex pipelines.

We can encode powerful

\section{Dish Overview}

\section{Related Work}
